opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-05-14 chapters/01_introduction.tex
Added structure information prediction references

% Predicting structure information with machine learning
Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting
lattice parameters, spacegroup \cite{Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021}, and crystallite size from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments [cite 2-3 papers, incl. ours].
The patterns observed in experiments suffer from a host of imperfections that need to be modeled accurately in order to be able to transfer models trained on simulated data to experimental patterns. This includes noise, background, preferred orientation of the sample, ...
Most approaches currently model these imperfections as a simple signal based on a heuristic functional form added to the simulated diffractograms.

>>>>

% Predicting structure information with machine learning
Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting
lattice parameters\cite{Dong2021, Chitturi2021, Habershon2004}, spacegroup \cite{Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021}, and crystallite size \cite{Dong2021, Chakraborty2021}from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments [cite 2-3 papers, incl. ours].
The patterns observed in experiments suffer from a host of imperfections that need to be modeled accurately in order to be able to transfer models trained on simulated data to experimental patterns. This includes noise, background, preferred orientation of the sample, ...
Most approaches currently model these imperfections as a simple signal based on a heuristic functional form added to the simulated diffractograms.

### 2024-05-14 chapters/03_SOTA_ML.tex
Added structure information prediction references

>>>>

Using simulated diffractograms based on structures from the ICSD, Lee et al. managed to train a deep convolutional neural network (CNN) that is able to classify occurring phases in diffractograms of a specific compound pool. \cite{Lee2020}
Park et al. reached a test accuracy of roughly 81\% for a CNN, which classifies space groups of simulated single-phase diffractograms. \cite{Park2017}
A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi et al.\cite{Chitturi2021} They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles.
